Public Gender Egalitarianism: A Dataset of Dynamic Comparative Public Opinion Toward Egalitarian Gender Roles in the Public Sphere

### 2020-12-09 paper/dcpo_gender_roles.Rmd
expand convergent validation para a bit; revise construct validation paras for length; clean up

<!-- This article proceeds with the following order.  -->
<!-- First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. -->
<!-- Next, we illustrate the data source we used to build our index. -->
<!-- Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. -->
<!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->

# Multi-Dimensionality in Gender Egalitarianism

Gender egalitarianism does not have only one dimension but a multi-dimension.
Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions.
For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not.
To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework.
Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting.
The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions.
However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have.

@@

To avoid any potential multidimensionality in the Public Gender Egalitarianism index, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
The complete list of gender egalitarianism items is included in the Appendix.]
Thus, the "Public" in the name of the index does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
We describe these source data in detail in the next section.

# The Source Data on Gender Egalitarian Attitudes

@@

Figure&nbsp;\ref{conv_plot} displays our tests of convergent validation.
Convergent validation refers to demonstrating that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years.
<!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
Then, in the center panel, we look at the question that provides most data-rich cross-section.
<!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country. 
<!-- Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country. -->
<!-- The U.S. General Social Survey asked this question 25 times from 1972 to 2016. -->
<!-- It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement. -->
In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S. GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.

@@

In Figure&nbsp;\ref{surv_const_plot}, we turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
For purposes of construct validation, we look first to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Although many of the items in this category are on their face at best only very tangentially related to public gender egalitarianism, others are plausibly causally related.
Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children."
As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more.
Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family." 
Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself.
(Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.)
If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In either case, though, they provide evidence of the validity of the PGE Mean scores.]
In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane.
The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence. 
With regard to all of these items, too, the correlations with the PGE Mean scores are strong.

@@

Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
Assuming that attitudes toward gender egalitarianism in the public sphere both cause and are caused by women's gains in the workplace, assessing the relationships between the mean PGE and measures of workplace gender equality provides construct validation of our measure.
In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the mean PGE index to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
In the right panel, we plot the mean PGE index against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
Both correlations are strong.
As with our tests of convergent validation, these tests of construct validation provide reassuring evidence of the validity of the mean PGE.

# Using the Public Gender Egalitarianism Index

One aspect of latent-variable estimates of public opinion like the PGE that is easy for researchers to overlook is the uncertainty in the estimates.
But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the mean PGE index---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
Therefore, taking the uncertainty in the mean and polarization PGE indexes into account is crucial to reaching well-grounded conclusions.

The PGE download includes pre-formatted data to facilitate incorporating the uncertainty in the indexes.
In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.
In Stata, the \texttt{mi estimate:} command prefix originally developed for analyzing multiply imputed data can be used to automate the process of building uncertainty into nearly any analysis.
Step-by-step instructions on how to use these tools, complete with examples, are included in the data download.

>>>>

<!-- This article proceeds with the following order.  -->
<!-- First, we discuss multi-dimensionality in egalitarian gender role and the reasons why we focus on the public sector. -->
<!-- Next, we illustrate the data source we used to build our index. -->
<!-- Then, the estimates of egalitarian gender role about 120 countries from 1972 to 2020 is introduced. -->
<!-- Lastly, we provide examples of how the new index about egalitarian gender role can be used and conclude.     -->
<!-- Gender egalitarianism does not have only one dimension but a multi-dimension. -->
<!-- Generating a measure of egalitarian gender roles without the classification may cause multidimensionality problem since people might have different opinions about gender roles by the dimensions. -->
<!-- For instance, some people have a more egalitarian veiw about the gender role in public sector rather than in private sector, while others do not. -->
<!-- To be specific, some might think that men and women should be treated and promoted equally at work, but that women should be in charge of housework. -->
<!-- Also, others may argue that both men and women can succeed as politicians, while saying that women are responsible for parenting. -->
<!-- The multi-dimensionality problem is relatively not salient if people in a society have an egalitarian view of all dimensions. -->
<!-- However, if we disregard this kind of multi-dimensionality given that there are some variations of gender egalitarain opinions by dimensions, we will not be able to measure gender egalitarianism properly in the various dimensions that people have. -->

# Focusing on Public Opinion Toward Gender Equality in the Public Sphere

@@

To avoid any potential multidimensionality in the Public Gender Egalitarianism data, we include only survey items corresponding to the first category, gender egalitarianism in the public sphere.^[Items that fell into both the first category and another, such as "A man's job is to earn money; a woman's job is to look after the home and family," which by explicitly counterposing the traditional gender roles suggests women unlike men should not earn money in the public sphere (while also suggesting that men unlike women should not look after home and family in the private sphere) were included in the PGE index.
The complete list of gender egalitarianism items is included in the Appendix.]
Thus, the "Public" in the name of the dataset does double duty, referring both to the fact that it measures the _public's_ attitudes on gender equality and to specifically its attitudes on this _public_ aspect of gender egalitarianism.
In all, we identified `r n_items` of these survey items that were asked in no fewer than five country-years in countries surveyed at least twice; these items were drawn from `r n_surveys` different survey datasets.
We describe these source data in detail in the next section.

# The Source Data on Public Gender Egalitarianism

@@

Figure&nbsp;\ref{conv_plot} displays our tests of convergent validation.
Convergent validation refers to demonstrating that a measure is empirically associated with alternative indicators of the same concept [@Adcock2001, 540].
Here, we compare PGE Mean scores to responses to individual survey items that were included in the source data, that is, we provide an "internal" validation test [see, e.g., @Caughey2019, 689; @Solt2020c, 10].
In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years.
<!-- In the left panel, we examine the `polileader4` question mentioned above, the most common item in the source data across all country-years, combining for this purpose all those who agreed or strongly agreed that "on the whole, men make better political leaders than women." -->
Then, in the center panel, we look at the question that provides most data-rich cross-section, the `poliequal3` item in Pew Global's Spring 2007 survey.
<!-- Then, in the center panel, we look at the question that provides most data-rich cross-section: the `poliequal3` item in Pew Global's Spring 2007 survey that asked whether respondents felt "men generally make better political leaders than women," vice versa, or whether "in general, women and men make equally good political leaders." -->
Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the item with the largest number of observations for a single country, the `emopoli2` survey item, which asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women." 
<!-- Finally, in the right panel, to evaluate how well the PGE Mean score captures change over time, we focus on the `emopoli2` survey item, the item with the largest number of observations for a single country. -->
<!-- The U.S. General Social Survey asked this question 25 times from 1972 to 2016. -->
<!-- It asks whether respondents agreed or disagreed that "most men are better suited emotionally for politics than are most women"; to facilitate visual comparison of the longitudinal relationship, we plot the estimated population proportion that disagreed with the statement. -->
In every case, the correlations---estimated taking into account the uncertainty in the measures^[The uncertainty in the PGE Mean score and in the percentage in the population who would agree with the item does not substantially affect the correlation with the `polileader4` question, but failing to account for this uncertainty would overstate the correlation with the Pew `poliequal3` item, at $R =$ `r with(internal_poliequal, cor(prop, mean)) %>% round(2)`, and the U.S. GSS `emopoli2` item, at $R =$ `r with(internal_us, cor(prop, mean, use = "pairwise.complete.obs")) %>% round(2)`.
We take up the issue of the importance of taking uncertainty into account when working with the PGE data in a subsequent section.]---are in the expected direction and very strong.

@@

We turn to construct validation, which refers to demonstrating, for some _other_ concept believed causally related to the concept a measure seeks to represent, that the measure is empirically associated with measures of that other concept [@Adcock2001, 542].
In Figure&nbsp;\ref{surv_const_plot}, we look to individual survey items from our third category of gender egalitarianism, that is, questions that ask how women should balance opportunities in the public sphere with their traditional duties in the private sphere.
Assuming that attitudes that women should prioritize housework and childcare over education, politics, and paid employment---or convictions that there will be negative consequences if they do not---will lead to less gender egalitarian opinions with regard to these latter, public-sphere activities, evidence for this theoretical relationship will provide construct validation for the PGE Mean score.
Exemplars of such items across all available country-years ("a job is alright but what most women really want is a home and children" from the WVS and EVS), in cross-section ("the most important role of a woman is to take care of her home and family" from the Eurobarometer 87.4), and in time series ("a pre-school child is likely to suffer if his or her mother works" from the German ALLBUS, WVS, and EVS) all show strong correlations with the PGE Mean scores.
<!-- Consider `wantch4`, an item depicted in the left pane asked by the World Values Survey and the European Values Survey, which asked respondents the extent to which they agree with the statement, "a job is alright but what most women really want is a home and children." -->
<!-- As agreement suggests that women do not truly care about opportunities in the workplace, those who do should be expected to be less likely to believe women should enjoy equal access to such opportunities which men implicitly value more. -->
<!-- Or, similarly, `familywoman4`, an item plotted in the center pane from Eurobarometer 87.4, which asked respondents the extent of their agreement with the statement, "the most important role of a woman is to take care of her home and family."  -->
<!-- Though not directly implying that women should not enjoy equal opportunities in education, politics, and the workplace, it may still be fairly surmised that those holding this position would consequently consider that, since opportunities beyond the home are of secondary importance for women, men should have priority.^[One might argue that these two questions, particularly the latter, rather than tapping a distinct concept causally related to public gender egalitarianism are in fact tapping aspects of public gender egalitarianism itself. -->
<!-- (Indeed, the `tradroles` series of questions, which couple the `familywoman4` stem with the idea that the most important role of a man is to earn money---and so more explicitly indicates that the public sphere is appropriately segregated by gender---is included among the items used to estimate the PGE data.) -->
<!-- If these two questions are thought of as indicators of public gender egalitarianism, then, because they are not included in the PGE source data, these plots constitute not construct validation but rather "external" convergent validation [see, e.g., @Caughey2019, 689; @Solt2020c, 10]. -->
<!-- In either case, though, they provide evidence of the validity of the PGE Mean scores.] -->
<!-- In a slightly different vein, `preschoolwork4`, included in the German ALLBUS, the World Values Survey, and the European Values Survey, asked respondents the extent to which they agreed that "a pre-school child is likely to suffer if his or her mother works;" we plot the time series of the proportion of the population of Germany estimated to disagree or disagree strongly with this statement in the right pane. -->
<!-- The belief that mothers working cause harm to their children should be expected to lead to disfavoring gender equality in workforce to avoid this purported negative consequence.  -->
<!-- With regard to all of these items, too, the correlations with the PGE Mean scores are strong. -->

@@

Finally, Figure&nbsp;\ref{construct_plot} shows additional tests of construct validation.
As attitudes toward gender egalitarianism in the public sphere plausibly both cause and are caused by women's gains in the workplace, strong relationships between the PGE Mean scores and measures of workplace gender equality provide construct validation for our measure.
In the left panel of Figure&nbsp;\ref{construct_plot}, we compare the PGE Mean scores to the ratio of women's to men's labor force participation rates in `r nrow(lfpr_un %>% filter(year == 2016))` countries in 2016, drawing on data compiled by the Statistics Division of the UN Department of Economic and Social Affairs [-@UNDESA2020].
In the right panel, we plot the PGE Mean scores against the percentage of women on the boards of directors of the largest publicly listed companies in `r nrow(directors)` countries in 2017 [see @OECD2020].
Both correlations are strong.
Together, this evidence of construct validation and convergent validation attests to the validity of the PGE Mean scores as measures of public opinion towards gender equality in the public sphere.

# Using the Public Gender Egalitarianism Dataset

One aspect of latent-variable estimates of public opinion like the PGE dataset that is easy for researchers to overlook is the uncertainty in the estimates.
But neglecting to incorporate this uncertainty by using only the mean estimate for each country-year---that is, for example, the mean of the PGE Mean scores---in an analysis can lead one to mistakenly conclude that the analysis supports the hypothesis [see @Tai2020] as well as to mistakenly conclude that it does _not_ support the hypothesis [see @Crabtree2015].
Therefore, taking the uncertainty in the PGE Mean and Polarization scores into account is crucial to reaching well-grounded conclusions.

The download includes pre-formatted data to facilitate incorporating the uncertainty in the PGE Mean and Polarization scores.
In R, the functions of the \texttt{purrr} package [@Henry2019, also included in the widely-used \texttt{tidyverse} package [@Wickham2017a]] make it entirely straightforward to incorporate the uncertainty of the PGE estimates.
In Stata, the \texttt{mi estimate:} command prefix originally developed for analyzing multiply imputed data can be used to automate the process of building uncertainty into nearly any analysis.
Step-by-step instructions on how to use these tools, complete with examples, are included in the data download.
